Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-24 src/2.GenericProgramming.tex
Chose->choose.

\begin{figure}[h]
\begin{Verbatim}[frame=leftline]
Constrained Semantics: memory allocations, memory movement, parallel kernels
Parallel Paradigms: patterns, tasks
Expression: language 
Control Paradigm: prescriptive, descriptive
\end{Verbatim}
\caption{Semantic capture: a set of constrained semantics, parallel paradigms, expression and concern define key properties a parallel programming model.}
\label{figSemCapture}
\end{figure}

@@

A parallel programming paradigm is an abstract representation with the purpose of facilitating the programmer's understanding of programming rules and program behavior. Which programming paradigm to chose depends on several considerations. Parallel patterns allow the programmer to permit concurrent execution for commonly occurring programming patterns such as loop constructs. Tasking is a paradigm that supports the expression of interdependent work items needed for irregular algorithms. Distributed and correctness-oriented programming models may implement actor-based programming, where each unit of execution represents an actor who communicates over predefined communication channels. This paradigm eliminates accesses to shared state and aligns well with message passing programming (MPI). The execution model and memory model aspects of a programming model define its behavior. That is, it defines the relationship between abstract concepts and program execution on the given architecture.

>>>>

\begin{figure}[h]
\begin{Verbatim}[frame=leftline]
Constrained Semantics: memory allocations, 
memory movement, execution parameters
Parallel Paradigms: patterns, tasks
Expression: language 
Control Paradigm: prescriptive, descriptive
\end{Verbatim}
\caption{Semantic capture: a set of constrained semantics, parallel paradigms, expression and concern define key properties a parallel programming model.}
\label{figSemCapture}
\end{figure}

@@

A parallel programming paradigm is an abstract representation with the purpose of facilitating the programmer's understanding of programming rules and program behavior. Which programming paradigm to choose depends on several considerations. Parallel patterns allow the programmer to permit concurrent execution for commonly occurring programming patterns such as loop constructs. Tasking is a paradigm that supports the expression of interdependent work items needed for irregular algorithms. Distributed and correctness-oriented programming models may implement actor-based programming, where each unit of execution represents an actor who communicates over predefined communication channels. This paradigm eliminates accesses to shared state and aligns well with message passing programming (MPI). The execution model and memory model aspects of a programming model define its behavior. That is, it defines the relationship between abstract concepts and program execution on the given architecture.
